### 2010-03-27 docs/architecture/architecture.tex
more reorganization to make it more into a User's Manual

\section{Running A Problem}

@@

@@

@@

\section{Visualization / Analysis}

\subsection{Amrvis}

\subsection{{\tt data\_processing} scripts}

\subsection{VisIt}

@@

\item {\tt extern/EOS/gamma\_law\_general} assumes an ideal gas with a mixed 
     composition and a constant ratio of specific heats, $\gamma$:
      \begin{eqnarray}
      e &=& \frac{p}{\rho (\gamma - 1) } \\
      p &=& \frac{\rho k_B T}{\mu m_p} 
      \end{eqnarray}
     where $k_B$ is Boltzmann's constant and $m_p$ is the mass of the
     proton.
     The mean molecular weight, $\mu$, is computed either assuming 
     electrically neutral atoms:
     \begin{equation}
     \mu = \left ( \sum_k \frac{X_k}{A_k} \right )^{-1}
     \end{equation}
     or complete ionization:
     \begin{equation}
     \mu = \left ( \sum_k \frac{X_k (Z_k + 1)}{A_k} \right )^{-1}
     \end{equation}
     The default is neutral, and presently one must change a parameter
     in the source code to switch between these limits.
\end{itemize}

>>>>

\section{Getting Started}

In this section we describe some of the standard problems that come
with MAESTRO, how to run the code, and how to look at the output.

@@

\subsection{Compiling and Running}

@@

\subsection{Common Runtime Parameters}

\subsection{Working with the Output}

Visualization and analysis are done with on the plotfiles.  The
frequency of plotfile outputting can be changed using the runtime
parameters {\tt plot\_int}, which specifies the number of steps
between output, and {\tt plot\_deltat} which specifies the simulation
time between output.  Setting {\tt plot\_int} to {\tt -1} disables
step-based outputting; setting {\tt plot\_deltat} to {\tt 0.0}
disables time-based outputting.

\subsubsection{Amrvis}

\subsubsection{{\tt data\_processing} scripts}

\subsubsection{VisIt}

@@

@@

\item {\tt extern/EOS/gamma\_law\_general} assumes an ideal gas with a mixed 
     composition and a constant ratio of specific heats, $\gamma$:
      \begin{equation}
      p = \rho e (\gamma - 1) = \frac{\rho k_B T}{\mu m_p} 
      \end{equation}
     where $k_B$ is Boltzmann's constant and $m_p$ is the mass of the
     proton.
     The mean molecular weight, $\mu$, is computed either assuming 
     electrically neutral atoms:
     \begin{equation}
     \mu = \left ( \sum_k \frac{X_k}{A_k} \right )^{-1}
     \end{equation}
     or complete ionization:
     \begin{equation}
     \mu = \left ( \sum_k \frac{X_k (Z_k + 1)}{A_k} \right )^{-1}
     \end{equation}
     The default is neutral, and presently one must change a parameter
     in the source code to switch between these limits.
\end{itemize}
